\textbf{CMCS 818J Project Final Report}

### 2012-12-19 doc/final_report/draft_report.tex

	In this report we will be describing a scheme for achieving a streaming authenticated data structure (SADS) proposed by Papamanthou and 
	Shi \cite{sads}. The goal of this project is twofold. First, we will be implementing an example of this data
	structure and second, we will be building an application using the SADS primitive.

@@

	In the verifiable computation (VC) problem, a client wishes to compute a complex
	function f on an input x. The client does not trust the server and therefore, would like to
	be able to verify the correctness of the computation without investing too much resources.
	The increasing use of distributed computing over the internet also makes strong servers more commonly 
	available. The growth of outsourcable computation in the form of cloud computing has attracted a renewed
	interest in the VC problem, and a considerable amount of research has been devoted to these problems \cite{evsc}.\\

	The introduced scheme, Streaming Authenticated Data Structure (SADS), does not require any interaction between the client and the server while the stream is observed.
	Three important properties are obtained using this scheme :
	\begin{enumerate}[a.]
	\item Independence of prover and verifier : the prover and the verifier update their status independently and with no interaction.
	\item Efficiency : It can be shown that an exponential improvement for many commonly queries in the prover's running time can be achieved.
	\item Expressiveness : a wide range of queries such as membership/ non-membership, successor, range search and frequencies can be supported using this scheme.
	\end{enumerate}

	The ultimate goal of the proposed scheme is to build secure protocols that enable the verification of computation
	that is performed by an untrusted resource.\\

	The rest of this paper is organized as follows. We will be describing streaming authenticated data structure 
	goals. Some recent research in streaming verifiable computation will be discussed. We then describe the 
	homomorphic property used in the the SADS scheme. Some definitions will be presented in the following section.
	We present significant features of our implementation afterwards followed by presenting the performance of 
	our investigation. Finally, we conclude our paper by providing some future plans.\\

@@

	The bottomline for the proposed scheme uses Merkle tree structure using a hash function that has the homomorphic
	property. A way to map the outputs to the input domain considers \textit{labels} and allocates the root digest as
	the sum of well defined functions, nameley, \textit{partial digests} applied to the leaves of the Merkle tree.
	This will ease for the felxibility and efficiency in streaming update for the verifier and prover. \\

	Each node in the tree has a label $\lambda$ and a digest \textit{d}, where a node's digest
	could be computed uniquely from its label. Given two children labels, the digest of the parent can be 
	calculated. Figure one represents this property. The labels are denoted by circles and digests are 
	represented with squares. \\

@@

	As an example, if the set of elements contains the nodes {1,4,6,7} the digest of the hash root of the tree 
	could be expressed as : \textit{D}(1)+\textit{D}(4)+\textit{D}(6)+\textit{D}(7)
        where \textit{D}(x) is the partial digest of the root with respect to x. \\

	The hash function is calculated as follows. Given a security parameter \textit{k}, $\textit{n} = 
	poly(\textit{k})$ and $\textit{q} $, $\textit{$\mu$}$, $\textit{$\beta$}$ outputed parameteres by the SADS 
	algorithm, $\textbf{L}, \textbf{R} \in Z $ two (k $\times$ m) random uniform matrices in \textit{mod q}, the 
	hashed function is defined as h(x,y)= $\textbf{L}$.x + $\textbf{R}$.y mod q. \\

@@

	The description of the SADS scheme reads much like a protocol, focusing on the behaviour of each of the prover and verifier during a streaming phase and a query phase.
	Before tackling the problem at the protocol level however, we must first implement the basic data structures each of the verifier and prover will need to perform their roles.
	This will be our starting point.

>>>>

	While Infrastructure and Platform -as-a-Service products provide clients access to large amounts of computing power and storage capacity, the client must trust the provider with their computation.
	It may be the case that verifying the computation requires too much resources and is infeasible for the client.
	In this report we will discuss a streaming setting in which a client and provider both witness a stream of data.
	In this setting the client is assumed to have limited resources in both storage and computational power, and as such, relies on the provider to serve as a database of sorts from which the client can query about the data stream.

	Papamanthou and Shi \cite{sads} proposed a scheme called Streaming Authenticated Data Structures, which allows the client to verify the provider answers his or her query correctly and does not tamper with the query results.
	The scheme has been shown to be secure and efficient requiring no communication between the client and the provider during the streaming setting.
	The goal of this project is twofold. First, we will be implementing an example of this data
	structure and second, we will be building an application using the SADS primitive.

@@

	In the verifiable computation (VC) problem, a client wishes to compute a complex function f on an input x.
	The client does not trust the server and therefore, would like to be able to verify the correctness of the computation without having to perform the computation themselves.
	The increasing use of distributed computing over the internet also makes strong servers more commonly available.
	The growth of outsourcable computation in the form of cloud computing has attracted a renewed interest in the VC problem, and a considerable amount of research has been devoted to these problems \cite{evsc}.

	The introduced scheme, Streaming Authenticated Data Structure (SADS), does not require any interaction between the client and the server while the stream is observed.
	Three important properties are obtained using this scheme :
	\begin{enumerate}[a.]
		\item Independence of prover and verifier : the prover and the verifier update their status independently and with no interaction.
		\item Efficiency : It can be shown that an exponential improvement for many commonly queries in the prover's running time can be achieved.
		\item Expressiveness : a wide range of queries such as membership/ non-membership, successor, range search and frequencies can be supported using this scheme.
	\end{enumerate} 
	The ultimate goal of the proposed scheme is to build secure protocols that enable the verification of computation 	that is performed by an untrusted resource.

	The rest of this paper is organized as follows. We will be describing streaming authenticated data structure goals.
	Some recent research in streaming verifiable computation will be discussed.
	We then describe the homomorphic property used in the the SADS scheme. Some definitions will be presented in the following section.
	We present significant features of our implementation afterwards followed by presenting the performance of our investigation.
	Finally, we conclude our paper by providing some future plans.

@@

	The bottomline for the proposed scheme uses Merkle tree structure using a hash function that has the homomorphic property.
	A way to map the outputs to the input domain considers \textit{labels} and allocates the root digest as	the sum of well defined functions, nameley, \textit{partial digests} applied to the leaves of the Merkle tree.
	This will ease for the felxibility and efficiency in streaming update for the verifier and prover.

	Each node in the tree has a label $\lambda$ and a digest \textit{d}, where a node's digest could be computed uniquely from its label.
	Given two children labels, the digest of the parent can be calculated. 
	Figure one represents this property. The labels are denoted by circles and digests are 
	represented with squares.

@@

	As an example, if the set of elements contains the nodes {1,4,6,7} the digest of the hash root of the tree 
	could be expressed as : \textit{D}(1)+\textit{D}(4)+\textit{D}(6)+\textit{D}(7)
        where \textit{D}(x) is the partial digest of the root with respect to x.

	The hash function is calculated as follows. Given a security parameter \textit{k}, $\textit{n} = 
	poly(\textit{k})$ and $\textit{q} $, $\textit{$\mu$}$, $\textit{$\beta$}$ outputed parameters by the SADS 
	algorithm, $\textbf{L}, \textbf{R} \in Z $ two (k $\times$ m) random uniform matrices in \textit{mod q}, the 
	hashed function is defined as h(x,y)= $\textbf{L}$.x + $\textbf{R}$.y mod q.

@@

	The description of the SADS scheme reads much like a protocol, focusing on the behavior of each of the prover and verifier during a streaming phase and a query phase.
	Before tackling the problem at the protocol level however, we must first implement the basic data structures each of the verifier and prover will need to perform their roles.
	This will be our starting point.
